### 2013-06-18 readme.Rmd
update readme

# highlightHTML

The aim of the `highlightHTML` package is to make it easy for users to customize HTML tables by using a single function that adds an `id` selector to the table cell tag.  The ability to customize the HTML table is limited the functionality of CSS and the user knowledge of CSS.   This package was motivated by latest push of using markdown documents which allow the user to focus on content instead of using something like LaTeX where choices between fonts and styling may take a larger role.  This package is motivated by that in that it allows a seemless way to interact with an HTML file to add table decoration.

## Usage
Installing the package:
```{r install, eval=FALSE}
library(devtools)
install_github(repo = "highlightHTML", username = "lebebr01")
```

This package post processes the html file produced from a markdown document.  Suppose you have a table like the following:

Color Name | Number
----------- | ------------
Blue | 5
Green | 35
Orange | 100
Red | 200

To use this package there are two steps, first indicate which cells you would like to change the appearance using CSS (i.e. background color, text color, etc.) by including the name of the id value to pass that cell or cells.  Using the above table example suppose we want to change the number column to blue and red for numbers less than 10 and greater than 150 respectively:

Color Name | Number
----------- | ------------
Blue | 5 #bgblue
Green | 35
Orange | 100
Red | 200 #bgred

The addition of the *#bgblue* and *#bgred* indicates which cells will be changed.  After turning the markdown document into an html file, this package can now be used to post-process the html file.  The post-processing will add an id value for each cell with the *#bgblue* or *#bgred* and remove those from the table.  This will look something like:

```{r function, eval=FALSE}
library(hightlightHTML)
highlightHTMLcells(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
```

This function should read in the html file to process.  Then it processes the file add the id tags to the specific cells identified.  Lastly if **updateCSS = TRUE**, then the tags will be added to the CSS of the document, otherwise if **FALSE** that will need to be added manually to the html file.  The file is then save to the output location, if no output location is given, the input file will be overwritten.

### 2013-06-18 R/highlightHTML.r
clean up and build documentation

@@ -9,14 +9,18 @@
 #' @param input File name of HTML file to highlight the cells of the table
 #' @param output Output file name of highlighted HTML file
 #' @param updateCSS TRUE/FALSE variable indicating whether the CSS should be updated.
-#' @parm tags character vector with CSS tags to be added
-#' @importFrom stringr str_replace_all
+#' @param tags character vector with CSS tags to be added
 #' @examples
-#' tmp <- c("<td> 100 #bgred </td>", "<td> 67 </td>", "<td> 32 #bgblue </td>", "<td> 12 #bgblue </td>", "<td> 55 </td>")
+#' # Example of simple test table
+#' # Change background color of table cells
+#' require(highlightHTML)
 #' tags <- c("#bgred {background-color: #FF0000;}", "#bgblue {background-color: #0000FF;}")
+#' highlightHTMLcells(input = "bgtable.html", output = "bgtable2.html", updateCSS = TRUE, tags = tags)
+#' # Change background color and text color
+#' tags <- c("#bgred {background-color: #FF0000; color: white;}", "#bgblue {background-color: #0000FF; color: white;}")
+#' highlightHTMLcells(input = "bgtable.html", output = "bgtable2.html", updateCSS = TRUE, tags = tags)
 #' @export 
 highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags) {
-  ## read in html file
   tmp <- readLines(input)
   
   CSSid <- gsub("\\{.+", "", tags)
@@ -42,3 +46,22 @@ highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags) {
   
   write(tmp, file = output)
 }
+
+
+#' Update external CSS file
+#' 
+#' @param input Name of the R object after readLines
+#' @param tags Character vector of tags to add to CSS
+updateCSS <- function(input, tags) {
+  
+  location <- grep("</style>", input)
+  
+  # # split file
+  tmpA <- input[1:(location-1)]
+  tmpB <- input[location:length(input)]
+  
+  ## adding custom CSS
+  tmp <- c(tmpA, tags, tmpB)
+  tmp
+}
+

### 2013-06-18 R/test.r

@@ -1,49 +1,0 @@
-# Entering in small test example
-tmp <- c("<td> 100 #bgred </td>", "<td> 67 </td>", "<td> 32 #bgblue </td>", "<td> 12 #bgblue </td>", "<td> 55 </td>")
-tags <- c("#bgred {background-color: #FF0000;}", "#bgblue {background-color: #0000FF;}")
-
-# Extracting CSS id values
-CSSid <- gsub("\\{.+", "", tags)
-CSSid <- gsub("^\\s+|\\s+$", "", CSSid)
-
-# Pasting CSS id values into HTML <td> tag - the for loop below does not include the CSSid part
-ids <- vector(mode = "character", length = length(CSSid))
-for(t in 1:length(CSSid)){
-  ids[t] <- paste("<td id=\'", CSSid[t], "\'>", sep = "")
-}
-
-
-#locations <- grep("#", tmp)
-
-for(p in 1:length(CSSid)){
-  locations <- grep(CSSid[p], tmp) # identifies location to place CSS id tag
-  
-  tmp[locations] <- gsub("<td>", ids[p], tmp[locations]) # replaces the HTML tag with CSS id included
-}
-
-#tmp[locations] <- gsub(CSSid[p], "", tmp[locations], fixed = TRUE)
-
-ids   # printing what the replacement should have been
-tmp   # Notice the blank part between the the single quotes, any idea why this didn't paste?
-
-# --------------------------------
-# This does work however
-
-# Entering in small test example
-tmp <- c("<td> 100 #bgred </td>", "<td> 67 </td>", "<td> 32 #bgblue </td>", "<td> 12 #bgblue </td>", "<td> 55 </td>")
-tags <- c("#bgred {background-color: #FF0000;}", "#bgblue {background-color: #0000FF;}")
-
-CSSid <- gsub("\\{.+", "", tags)
-CSSid <- gsub("^\\s+|\\s+$", "", CSSid)
-CSSid2 <- paste(" ", CSSid, sep = "")
-
-ids <- paste('<td id=', CSSid, '>', sep = "")
-
-for(i in 1:length(CSSid)){
-  locations <- grep(CSSid[i], tmp)  # finds locations to add id values
-  tmp[locations] <- gsub("<td>", ids[i], tmp[locations])  # adds the id values
-  tmp[locations] <- gsub(CSSid2[i], "", tmp[locations], fixed = TRUE)
-}
-
-ids 
-tmp

### 2013-06-18 R/updateCSS.r

@@ -1,16 +1,0 @@
-#' Update external CSS file
-#' 
-#' @param input Name of the R object after readLines
-#' @param tags Character vector of tags to add to CSS
-updateCSS <- function(input, tags) {
-  
-  location <- grep("</style>", input)
-  
- # # split file
-  tmpA <- input[1:(location-1)]
-  tmpB <- input[location:length(input)]
-  
-  ## adding custom CSS
-  tmp <- c(tmpA, tags, tmpB)
-  tmp
-}

### 2013-06-19 R/rgb2hex.r
rgb2hex function

@@ -1,0 +1,45 @@
+#' Convert RGB to hex
+#' 
+#' Enter a list of RGB color codes, or R colors, and get the appropriate hex color code.
+#' 
+#' @param rgbcode List of rgb color codes, each list must be a vector of three objects representing
+#'   the three components of rgb color code from 0 - 255.
+#' @param rcolor A list of R color names
+#' @examples 
+#' rgb2hex(rcolor = list("sienna2", "thistle1"))
+#' rgb2hex(rcolor = list("sienna2", "thistle1"), rgbcode = list('orange' = c(238, 74, 24), 
+#' 'raw umber' = c(113, 75, 35)))
+#' rgb2hex(rgbcode = list('orange' = c(238, 74, 24), 'raw umber' = c(113, 75, 35)))
+#' @export 
+rgb2hex <- function(rgbcode = NULL, rcolor = NULL) {
+  
+  if(is.null(rcolor) == FALSE){
+    if(is.list(rcolor) == FALSE) { rcolor <- as.list(rcolor) }
+    tmp <- lapply(lapply(rcolor, col2rgb), as.numeric)
+  }
+  
+  if(is.null(rcolor) == TRUE & is.null(rgbcode) == FALSE){ 
+    tmp <- rgbcode 
+  }
+  
+  if(is.null(names(rgbcode)) == TRUE) {
+    namescol <- paste("Color ", 1:length(rgbcode), sep = "")
+  } else {
+    namescol <- names(rgbcode)
+  }
+  
+  if(is.null(rcolor) == FALSE & is.null(rgbcode) == FALSE){
+    tmp <- c(rgbcode, tmp)
+    namescol <- c(names(rgbcode), rcolor)
+  }
+  
+  if(is.null(rcolor) == FALSE & is.null(rgbcode) == TRUE){
+    namescol <- rcolor
+  }  
+  
+  names(tmp) <- namescol
+
+  hex <- sapply(lapply(tmp, sprintf, fmt = "%X"), paste, collapse = "")
+  hexP <- data.frame(HexCodes = hex)
+  hexP
+}

### 2013-11-21 R/highlightHTML.r
fix file path and clean up examples

@@ -14,11 +14,29 @@
 #' # Example of simple test table
 #' # Change background color of table cells
 #' require(highlightHTML)
-#' tags <- c("#bgred {background-color: #FF0000;}", "#bgblue {background-color: #0000FF;}")
-#' highlightHTMLcells(input = "bgtable.html", output = "bgtable2.html", updateCSS = TRUE, tags = tags)
-#' # Change background color and text color
-#' tags <- c("#bgred {background-color: #FF0000; color: white;}", "#bgblue {background-color: #0000FF; color: white;}")
-#' highlightHTMLcells(input = "bgtable.html", output = "bgtable2.html", updateCSS = TRUE, tags = tags)
+#' 
+#' # Setting path for example html files 
+#' # To see path where these are saved, type file1 or file2 in the 
+#' # r console.
+#' file <- system.file('examples', package = 'highlightHTML')
+#' file1 <- paste(file, "bgtable.html", sep = "/")
+#' file2 <- paste(file, "bgtable2.html", sep = "/")
+#' 
+#' # Creating CSS tags to inject into HTML document
+#' tags <- c("#bgred {background-color: #FF0000;}", 
+#'   "#bgblue {background-color: #0000FF;}")
+#'   
+#' # Command to post-process HTML file
+#' highlightHTMLcells(input = file1, output = file2, updateCSS = TRUE, 
+#'   tags = tags)
+#'   
+#' # Change background color and text color with CSS
+#' tags <- c("#bgred {background-color: #FF0000; color: white;}", 
+#'   "#bgblue {background-color: #0000FF; color: white;}")
+#'   
+#' # Post-process HTML file
+#' highlightHTMLcells(input = file1, output = file2, updateCSS = TRUE, 
+#'   tags = tags)
 #' @export 
 highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags) {
   tmp <- readLines(input)

### 2013-11-21 R/runShinyApp.r

@@ -3,6 +3,7 @@
 #' Function that automatically opens shiny app to convert rgb codes to hexidecimal codes
 #' 
 #' @param ... Other arguments to pass, currently does nothing.
+#' @importFrom shiny runApp
 #' @export 
 shinyRGB2hex <- function(...) {
   shiny::runApp(system.file('shiny', package = 'highlightHTML'))

### 2013-11-21 R/highlightHTML.r
added browse arg to highlightHTMLcells function, set to TRUE by default to open output file

@@ -10,6 +10,8 @@
 #' @param output Output file name of highlighted HTML file
 #' @param updateCSS TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
+#' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
+#'    file is written, but not opened in browser. 
 #' @examples
 #' # Example of simple test table
 #' # Change background color of table cells
@@ -37,8 +39,12 @@
 #' # Post-process HTML file
 #' highlightHTMLcells(input = file1, output = file2, updateCSS = TRUE, 
 #'   tags = tags)
+#' 
+#' # By default the new file is opened in your default browser, herer set to FALSE
+#' highlightHTMLcells(input = file1, output = file2, updateCSS = TRUE,
+#'   tags = tags, browse=FALSE)
 #' @export 
-highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags) {
+highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags, browse=TRUE) {
   tmp <- readLines(input)
   
   CSSid <- gsub("\\{.+", "", tags)
@@ -63,6 +69,9 @@ highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags) {
   }
   
   write(tmp, file = output)
+
+  if(browse)
+    browseURL(output)
 }
 
 

### 2016-09-27 R/highlightHTML.r
Edit documentation.

@@ -44,6 +44,7 @@
 #' # By default the new file is opened in your default browser, here set to FALSE
 #' highlightHTMLcells(input = file1, output = tempfile(fileext = ".html"), updateCSS = TRUE,
 #'   tags = tags, browse=FALSE, print = FALSE)
+#' @importFrom utils browseURL
 #' @export 
 highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags, browse = TRUE, 
                                print = FALSE) {
@@ -118,6 +119,7 @@ highlightHTMLcells <- function(input, output, updateCSS = TRUE, tags, browse = T
 #' # Post-process HTML file
 #' highlightHTMLtext(input = file1, output = NULL, updateCSS = TRUE, 
 #'   tags = tags, browse = TRUE)
+#' @importFrom utils browseURL
 #' @export 
 highlightHTMLtext <- function(input, output, updateCSS = TRUE, tags, browse = TRUE, 
                               print = FALSE){

### 2016-09-27 R/highlightHTMLmaster.r

@@ -18,13 +18,14 @@
 #'    filtered to other methods (see browse or output).
 #' 
 #' @export
-highlightHTML <- function(input, output, updateCSS = TRUE, tags, browse = TRUE) {
+highlightHTML <- function(input, output, updateCSS = TRUE, tags, browse = TRUE, 
+                          print = FALSE) {
   
   tmp2 <- readLines(input)
   
   tmp2 <- highlightHTMLcells(input = tmp2, output = output, updateCSS = FALSE, 
                        tags, browse = FALSE, print = TRUE)
-  highlightHTMLtext(input = tmp2, output, updateCSS, tags, browse)
+  highlightHTMLtext(input = tmp2, output, updateCSS, tags, browse, print)
   
   
 }

### 2016-09-27 R/print.highlightHTML.r

@@ -2,7 +2,6 @@
 #' 
 #' Prints highlightHTML object
 #' 
-#' @export
 print.highlightHTML <- function(x, ...) {
   cat(format(x, ...), sep = "\n")
 }

### 2016-09-27 R/rgb2hex.r

@@ -10,6 +10,7 @@
 #' rgb2hex(rcolor = list("sienna2", "thistle1"), rgbcode = list('orange' = c(238, 74, 24), 
 #' 'raw umber' = c(113, 75, 35)))
 #' rgb2hex(rgbcode = list('orange' = c(238, 74, 24), 'raw umber' = c(113, 75, 35)))
+#' @importFrom grDevices col2rgb 
 #' @export 
 rgb2hex <- function(rgbcode = NULL, rcolor = NULL) {
   

### 2016-09-27 R/runShinyApp.r

@@ -3,7 +3,6 @@
 #' Function that automatically opens shiny app to convert rgb codes to hexidecimal codes
 #' 
 #' @param ... Other arguments to pass, currently does nothing.
-#' @importFrom shiny runApp
 #' @export 
 shinyRGB2hex <- function(...) {
   shiny::runApp(system.file('shiny', package = 'highlightHTML'))

### 2016-09-27 R/highlightHTML.r
fix examples to pass cran checks

@@ -6,50 +6,19 @@
 #' coming from a markdown or R markdown file to highlight certain cells based on a specific criteria,
 #' such as values greater than 85 should be highlighted as blue or text color changed to green.
 #' 
-#' @param input File name of HTML file to highlight the cells of the table
+#' @param x File name of HTML file to highlight the cells of the table
 #' @param output Output file name of highlighted HTML file
-#' @param updateCSS TRUE/FALSE variable indicating whether the CSS should be updated.
+#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print locical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
-#' @examples
-#' # Example of simple test table
-#' # Change background color of table cells
-#' require(highlightHTML)
-#' 
-#' # Setting path for example html files 
-#' # To see path where these are saved, type file or file1 in the 
-#' # r console.
-#' file <- system.file('examples', package = 'highlightHTML')
-#' file1 <- paste(file, "bgtable.html", sep = "/")
-#' 
-#' # Creating CSS tags to inject into HTML document
-#' tags <- c("#bgred {background-color: #FF0000;}", 
-#'   "#bgblue {background-color: #0000FF;}")
-#'   
-#' # Command to post-process HTML file - Writes to temporary file
-#' highlightHTMLcells(input = file1, output = tempfile(fileext = ".html"), updateCSS = TRUE, 
-#'   tags = tags, browse = FALSE)
-#'   
-#' # Change background color and text color with CSS
-#' tags <- c("#bgred {background-color: #FF0000; color: white;}", 
-#'   "#bgblue {background-color: #0000FF; color: white;}")
-#'   
-#' # Post-process HTML file
-#' highlightHTMLcells(input = file1, output = NULL, updateCSS = TRUE, 
-#'   tags = tags, browse = TRUE, print = FALSE)
-#' 
-#' # By default the new file is opened in your default browser, here set to FALSE
[…]

### 2016-09-27 R/highlightHTMLmaster.r

@@ -8,24 +8,69 @@
 #' a specific criteria.  This function handles both tables as well as normal text.  
 #' The options are only limited based on your knowledge of CSS.
 #' 
-#' @param input File name of HTML file to highlight the cells of the table
+#' @param input File name of HTML file to highlight the cells of the table or text
 #' @param output Output file name of highlighted HTML file
-#' @param updateCSS TRUE/FALSE variable indicating whether the CSS should be updated.
+#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print logical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
+#' @examples
+#' # Example of simple test table
+#' # Change background color of table cells
+#' library(highlight_html)
 #' 
+#' # Setting path for example html files 
+#' # To see path where these are saved, type file or file1 in the 
+#' # r console.
+#' file <- system.file('examples', package = 'highlight_html')
+#' file1 <- paste(file, "bgtable.html", sep = "/")
+#' 
+#' # Creating CSS tags to inject into HTML document
+#' tags <- c("#bgred {background-color: #FF0000;}", 
+#'   "#bgblue {background-color: #0000FF;}")
+#'   
+#' # Command to post-process HTML file - Writes to temporary file
+#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
+#'   tags = tags, browse = FALSE)
+#'   
+#' # Change background color and text color with CSS
+#' tags <- c("#bgred {background-color: #FF0000; color: white;}", 
+#'   "#bgblue {background-color: #0000FF; color: white;}")
+#'   
+#' # Post-process HTML file
+#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
+#'   tags = tags, browse = TRUE, print = FALSE)
+#' 
+#' # By default the new file is opened in your default browser, here set to FALSE
+#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE,
+#'   tags = tags, browse = FALSE, print = FALSE)
+#'   
+#' # Setting path for example html files 
[…]

### 2016-09-27 R/print.highlightHTML.r

@@ -2,6 +2,9 @@
 #' 
 #' Prints highlightHTML object
 #' 
+#' @param x An object from highlightHTML function.
+#' @param ... Additional arguments passed to function.
+#' 
 print.highlightHTML <- function(x, ...) {
   cat(format(x, ...), sep = "\n")
 }

### 2016-09-27 readme.Rmd
fix file path and clean up examples
update README

@@
 library(devtools)
-install_github(repo = "highlightHTML", username = "lebebr01")
+install_github('lebebr01/highlightHTML')
 ```
@@
 library(hightlightHTML)
-highlightHTMLcells(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
+highlight_html(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
 ```

### 2016-09-27 R/highlightHTMLmaster.r
fix typo package name examples

@@ -19,7 +19,7 @@
 #' @examples
 #' # Example of simple test table
 #' # Change background color of table cells
-#' library(highlight_html)
+#' library(highlightHTML)
 #' 
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 

### 2016-09-27 R/highlightHTMLmaster.r
add donttest

@@ -17,6 +17,7 @@
 #' @param print logical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
 #' @examples
+#' \donttest{
 #' # Example of simple test table
 #' # Change background color of table cells
 #' library(highlightHTML)
@@ -61,6 +62,7 @@
 #' # Post-process HTML file
 #' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
 #'   tags = tags, browse = TRUE)
+#' }
 #'   
 #' @export
 highlight_html <- function(input, output, update_css = TRUE, tags, browse = TRUE, 

### 2016-10-04 R/highlightHTMLmaster.r
Initialize unit testing and fix examples code.

@@ -25,8 +25,7 @@
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 
 #' # r console.
-#' file <- system.file('examples', package = 'highlight_html')
-#' file1 <- paste(file, "bgtable.html", sep = "/")
+#' file <- system.file('examples', 'bgtable.html', package = 'highlightHTML')
 #' 
 #' # Creating CSS tags to inject into HTML document
 #' tags <- c("#bgred {background-color: #FF0000;}", 
@@ -51,8 +50,7 @@
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 
 #' # r console.
-#' file <- system.file('examples', package = 'highlight_html')
-#' file1 <- paste(file, "bgtext.html", sep = "/")
+#' file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
 #' 
 #' # Change background color and text color with CSS
 #' tags <- c("#bgblack {background-color: black; color: white;}", 

### 2016-10-04 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(highlightHTML)
+
+test_check("highlightHTML")

### 2016-10-04 tests/testthat/test_structure.r

@@ -1,0 +1,15 @@
+context('test structure')
+
+test_that('correct print structure', {
+  file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
+  
+  # Change background color and text color with CSS
+  tags <- c("#bgblack {background-color: black; color: white;}", 
+            "#bgblue {background-color: #0000FF; color: white;}",
+            "#colgreen {color: green;}")
+  
+  # Post-process HTML file
+  tmp <- highlight_html(input = file, output = tempfile(fileext = ".html"), update_css = TRUE, 
+                 tags = tags, browse = FALSE, print = TRUE)
+  expect_true(is.character(tmp))
+})

### 2016-10-04 R/rgb2hex.r
Add unit tests for rgb2hex and simplify if syntax.

@@ -14,27 +14,27 @@
 #' @export 
 rgb2hex <- function(rgbcode = NULL, rcolor = NULL) {
   
-  if(is.null(rcolor) == FALSE){
-    if(is.list(rcolor) == FALSE) { rcolor <- as.list(rcolor) }
+  if(!is.null(rcolor)){
+    if(!is.list(rcolor)) { rcolor <- as.list(rcolor) }
     tmp <- lapply(lapply(rcolor, col2rgb), as.numeric)
   }
   
-  if(is.null(rcolor) == TRUE & is.null(rgbcode) == FALSE){ 
+  if(is.null(rcolor) & !is.null(rgbcode)){ 
     tmp <- rgbcode 
   }
   
-  if(is.null(names(rgbcode)) == TRUE) {
+  if(is.null(names(rgbcode))) {
     namescol <- paste("Color ", 1:length(rgbcode), sep = "")
   } else {
     namescol <- names(rgbcode)
   }
   
-  if(is.null(rcolor) == FALSE & is.null(rgbcode) == FALSE){
+  if(!is.null(rcolor) & !is.null(rgbcode)){
     tmp <- c(rgbcode, tmp)
     namescol <- c(names(rgbcode), rcolor)
   }
   
-  if(is.null(rcolor) == FALSE & is.null(rgbcode) == TRUE){
+  if(!is.null(rcolor) & is.null(rgbcode)){
     namescol <- rcolor
   }  
   

### 2016-10-04 tests/testthat/test_rgb.r

@@ -1,0 +1,8 @@
+context('test rgb')
+
+test_that('correct structure', {
+  expect_equal(nrow(rgb2hex(rcolor = list('sienna2', 'thistle1'))), 2)
+  expect_equal(nrow(rgb2hex(rcolor = list("sienna2", "thistle1"), 
+                            rgbcode = list('orange' = c(238, 74, 24),
+                                           'raw umber' = c(113, 75, 35)))), 4)
+})

### 2016-10-24 R/table_inject.r
finalize table inject and bump version

@@ -7,6 +7,20 @@
 #' @param conditions A vector of conditions to include id. Must be same length as id
 #' @param variable An optional vector of column names to specify search of conditions.
 #' @export
+#' 
+#' @examples 
+#' library(dplyr)
+#' library(highlightHTML)
+#'
+#' summ_table <- mtcars %>% 
+#'   group_by(cyl) %>% 
+#'   summarise(avg_mpg = mean(mpg), sd_mpg = sd(mpg)) %>%
+#'   data.frame()
+#'   
+#'   table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+#'   conditions = c('< 2', '> 16'))
+#'   
+
 table_id_inject <- function(x, id, conditions, variable = NULL) {
   
   if(is.null(variable)) {
@@ -21,9 +35,12 @@ table_id_inject <- function(x, id, conditions, variable = NULL) {
     ifelse(eval(parse(text = paste_cond[[xx]])), TRUE, FALSE))
   
   x2 <- x
-  lapply(seq_along(locations), function(xx) 
-      x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])
-    )
+  for(xx in seq_along(locations)) {
+    x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])
+  }
+  # lapply(seq_along(locations), function(xx) 
+  #     x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])
+  #   )
   
-  list(x, x2)
+  return(x2)
 }

### 2016-10-25 R/table_inject.r
Remove redundant line in table inject function.

@@ -33,14 +33,13 @@ table_id_inject <- function(x, id, conditions, variable = NULL) {
   
   locations <- lapply(seq_along(id), function(xx) 
     ifelse(eval(parse(text = paste_cond[[xx]])), TRUE, FALSE))
-  
-  x2 <- x
+
   for(xx in seq_along(locations)) {
-    x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])
+    x[locations[[xx]] == TRUE] <- paste(xs[locations[[xx]] == TRUE], id[xx])
   }
   # lapply(seq_along(locations), function(xx) 
   #     x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])
   #   )
   
-  return(x2)
+  return(x)
 }

### 2016-10-25 R/table_inject.r
fix typo

@@ -35,7 +35,7 @@ table_id_inject <- function(x, id, conditions, variable = NULL) {
     ifelse(eval(parse(text = paste_cond[[xx]])), TRUE, FALSE))
 
   for(xx in seq_along(locations)) {
-    x[locations[[xx]] == TRUE] <- paste(xs[locations[[xx]] == TRUE], id[xx])
+    x[locations[[xx]] == TRUE] <- paste(x[locations[[xx]] == TRUE], id[xx])
   }
   # lapply(seq_along(locations), function(xx) 
   #     x2[locations[[xx]] == TRUE] <- paste(x2[locations[[xx]] == TRUE], id[xx])

### 2016-10-27 R/highlightHTML.r
update order of arguments to put required arguments first.

@@ -8,16 +8,16 @@
 #' 
 #' @param x File name of HTML file to highlight the cells of the table
 #' @param output Output file name of highlighted HTML file
-#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
+#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print locical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
 #' @importFrom utils browseURL
 #' @export 
-highlight_html_cells <- function(x, output, update_css = TRUE, tags, browse = TRUE, 
-                               print = FALSE) {
+highlight_html_cells <- function(x, output, tags, update_css = TRUE, 
+                                 browse = TRUE, print = FALSE) {
   
   CSSid <- gsub("\\{.+", "", tags)
   CSSid <- gsub("^[\\s+]|\\s+$", "", CSSid)
@@ -58,16 +58,16 @@ highlight_html_cells <- function(x, output, update_css = TRUE, tags, browse = TR
 #' 
 #' @param x File name of HTML file to highlight the cells of the table
 #' @param output Output file name of highlighted HTML file
-#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
+#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print locical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
 #' @importFrom utils browseURL
 #' @export 
-highlight_html_text <- function(x, output, update_css = TRUE, tags, browse = TRUE, 
-                              print = FALSE){
+highlight_html_text <- function(x, output, tags, update_css = TRUE, 
+                                browse = TRUE, print = FALSE){
   
   CSSid <- gsub("\\{.+", "", tags)
   CSSid <- gsub("^[\\s+]|\\s+$", "", CSSid)

### 2016-10-27 R/highlightHTMLmaster.r

@@ -10,8 +10,8 @@
 #' 
 #' @param input File name of HTML file to highlight the cells of the table or text
 #' @param output Output file name of highlighted HTML file
-#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated.
 #' @param tags character vector with CSS tags to be added
+#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print logical, if TRUE print output to R console, if false (default) output is 
@@ -32,20 +32,20 @@
 #'   "#bgblue {background-color: #0000FF;}")
 #'   
 #' # Command to post-process HTML file - Writes to temporary file
-#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
-#'   tags = tags, browse = FALSE)
+#' highlight_html(input = file, output = tempfile(fileext = ".html"),  
+#'   tags = tags, update_css = TRUE, browse = FALSE)
 #'   
 #' # Change background color and text color with CSS
 #' tags <- c("#bgred {background-color: #FF0000; color: white;}", 
 #'   "#bgblue {background-color: #0000FF; color: white;}")
 #'   
 #' # Post-process HTML file
-#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
-#'   tags = tags, browse = TRUE, print = FALSE)
+#' highlight_html(input = file, output = tempfile(fileext = ".html"),  
+#'   tags = tags, update_css = TRUE, browse = TRUE, print = FALSE)
 #' 
 #' # By default the new file is opened in your default browser, here set to FALSE
-#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE,
-#'   tags = tags, browse = FALSE, print = FALSE)
+#' highlight_html(input = file, output = tempfile(fileext = ".html"), 
+#'   tags = tags, update_css = TRUE, browse = FALSE, print = FALSE)
 #'   
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 
@@ -58,20 +58,20 @@
 #'   "#colgreen {color: green;}")
 #'   
 #' # Post-process HTML file
-#' highlight_html(input = file1, output = tempfile(fileext = ".html"), update_css = TRUE, 
-#'   tags = tags, browse = TRUE)
[…]

### 2016-10-27 vignettes/the_basics.R
Finalize first draft of vignette.

@@ -1,0 +1,25 @@
+## ----function, eval=FALSE------------------------------------------------
+#  library(hightlightHTML)
+#  file <- system.file('examples', 'bgtable.html',
+#                      package = 'highlightHTML')
+#  tags <- c("#bgred {background-color: #FF0000;}",
+#    "#bgblue {background-color: #0000FF;}")
+#  highlight_html(input = file,
+#                 output = tempfile(fileext = ".html"),
+#                 tags = tags,
+#                 update_css = TRUE,
+#                 browse = TRUE,
+#                 print = FALSE)
+
+## ----text, eval = FALSE--------------------------------------------------
+#  file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
+#  
+#  # Change background color and text color with CSS
+#  tags <- c("#bgblack {background-color: black; color: white;}",
+#    "#bgblue {background-color: #0000FF; color: white;}",
+#    "#colgreen {color: green;}")
+#  
+#  # Post-process HTML file
+#  highlight_html(input = file, output = tempfile(fileext = ".html"),
+#                 tags = tags, update_css = TRUE, browse = TRUE)
+

### 2016-10-28 R/highlightHTMLmaster.r
Add render function to highlight_html

@@ -8,7 +8,8 @@
 #' a specific criteria.  This function handles both tables as well as normal text.  
 #' The options are only limited based on your knowledge of CSS.
 #' 
-#' @param input File name of HTML file to highlight the cells of the table or text
+#' @param input File name of HTML file to highlight the cells of the table or text. 
+#'    Alternatively, if render = TRUE, a Rmd or md file can be specified as the input.
 #' @param output Output file name of highlighted HTML file
 #' @param tags character vector with CSS tags to be added
 #' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated
@@ -16,6 +17,8 @@
 #'    file is written, but not opened in browser. 
 #' @param print logical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
+#' @param render logical, if TRUE will call the rmarkdown::render() function to 
+#'    convert Rmd or md files to html prior to injecting CSS.
 #' @examples
 #' \donttest{
 #' # Example of simple test table
@@ -60,13 +63,28 @@
 #' # Post-process HTML file
 #' highlight_html(input = file, output = tempfile(fileext = ".html"), 
 #'   tags = tags, update_css = TRUE, browse = TRUE)
+#'   
+#' # Use of render
+#' file <- system.file('examples', 'mwe.md', package = 'highlightHTML')
+#' tags <- c("#bgred {background-color: #FF0000; color: white;}",
+#'    "#bgblue {background-color: #0000FF; color: white;}",
+#'    "#bgblack {background-color: #000000; color: white;}",
+#'    "#colgold {color: #FFD700;}")
+#' highlight_html(input = file, output = tempfile(fileext = '.html'),
+#'   tags = tags, update_css = TRUE, browse = TRUE, render = TRUE)
 #' }
 #'   
 #' @export
 highlight_html <- function(input, output, tags, update_css = TRUE, 
-                           browse = TRUE, print = FALSE) {
-  
-  tmp2 <- readLines(input)
+                           browse = TRUE, print = FALSE,
+                           render = FALSE) {
+  if(render) {
+    rmarkdown::render(input = input, output_format = 'html_document',
+                      output_file = output)
+    tmp2 <- readLines(output)
+  } else {
+    tmp2 <- readLines(input)
+  }
   
   tmp2 <- highlight_html_cells(x = tmp2, output = output, tags,
                                update_css = FALSE, 

### 2017-01-03 readme.Rmd
add build badge to readme
update readme with codecov badge
Bump to rerun travis.ci
Update to add badge to README.

@@
 # highlightHTML
+
+[![Build Status](https://travis-ci.org/lebebr01/highlightHTML.svg?branch=master)](https://travis-ci.org/lebebr01/highlightHTML)
+[![codecov.io](https://codecov.io/github/lebebr01/highlightHTML/coverage.svg?branch=master)](https://codecov.io/github/lebebr01/highlightHTML?branch=master)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](http://cran.r-project.org/package=highlightHTML)
 

### 2017-01-31 R/table_inject.r
Closes #4

@@ -59,7 +59,8 @@ table_id_inject <- function(x, id, conditions, variable = NULL) {
                                 variable[[xx]][[ii]]])
         }
         x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]] <- 
-          paste(x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]], id[xx])
+          paste(unlist(x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]]), 
+                       id[xx])
       }
     }
   }

### 2017-01-31 R/table_inject.r
Need unlist in one more spot to completely fix #4

@@ -55,8 +55,8 @@ table_id_inject <- function(x, id, conditions, variable = NULL) {
         if(any(grepl("#", x[locations[[xx]][[ii]] == TRUE, 
                             variable[[xx]][[ii]]]))) {
           x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]] <-
-            gsub("\\s+#.+", "", x[locations[[xx]][[ii]] == TRUE, 
-                                variable[[xx]][[ii]]])
+            gsub("\\s+#.+", "", unlist(x[locations[[xx]][[ii]] == TRUE, 
+                                variable[[xx]][[ii]]]))
         }
         x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]] <- 
           paste(unlist(x[locations[[xx]][[ii]] == TRUE, variable[[xx]][[ii]]]), 

### 2017-01-31 vignettes/the_basics.R
Add compiled versions of vignettes

@@ -1,5 +1,5 @@
 ## ----function, eval=FALSE------------------------------------------------
-#  library(hightlightHTML)
+#  library(highlightHTML)
 #  file <- system.file('examples', 'bgtable.html',
 #                      package = 'highlightHTML')
 #  tags <- c("#bgred {background-color: #FF0000;}",

### 2017-01-31 inst/examples/joss.Rmd
Documents for JOSS Submission Prep.

---
title: "Rmd to HTML"
author: "Brandon LeBeau"
date: "January 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple Markup
The `highlightHTML` packages allows for {#bggrey simple markup} to add formatting to text and tables. Using the `rmarkdown` package and the `table_id_inject` function allows users to easily add markup to Rmd documents and render directly to HTML.

```{r symm, echo = FALSE}
library(dplyr)
library(highlightHTML)

chick_tab <- chickwts %>%
  group_by(feed) %>%
  summarise(avg_weight = mean(weight),
            sd_weight = sd(weight))

table_id_inject(chick_tab, id = c('#bggrey', '#bgblack'), 
                conditions = c('> 270', '> 300'),
                variable = list('avg_weight', 'avg_weight'))
```

### 2017-01-31 vignettes/the_basics.R
Update to add example of R Markdown to HTML directly.

@@ -23,3 +23,14 @@
 #  highlight_html(input = file, output = tempfile(fileext = ".html"),
 #                 tags = tags, update_css = TRUE, browse = TRUE)
 
+## ----html, eval = FALSE--------------------------------------------------
+#  file <- system.file('examples', 'joss.Rmd', package = 'highlightHTML')
+#  
+#  tags <- c('#bgblack {background-color: black; color: white;}',
+#            '#bggrey {background-color: #d3d3d3;}',
+#            '#bglightred {background-color: #FF6666;}')
+#  
+#  highlight_html(input = file, output = tempfile(fileext = ".html"),
+#                 tags = tags, update_css = TRUE, browse = TRUE,
+#                 render = TRUE)
+

### 2017-01-31 inst/examples/joss.Rmd
Update on JOSS paper submission.

@@
 
-```{r symm, echo = FALSE}
+```{r symm, echo = FALSE, results = 'asis'}
 library(dplyr)
@@
 
-table_id_inject(chick_tab, id = c('#bggrey', '#bgblack'), 
-                conditions = c('> 270', '> 300'),
-                variable = list('avg_weight', 'avg_weight'))
+knitr::kable(table_id_inject(chick_tab, id = c('#bggrey', '#bgblack', '#bglightred'), 
+                conditions = c('> 270', '> 300', '> 60'),
+                variable = list('avg_weight', 'avg_weight', 'sd_weight')),
+             format = 'markdown')
 ```

### 2017-03-06 readme.Rmd
Edit of README for JOSS.

@@
 
-## Usage 
+## Installation 
 Installing the package:
 ```{r install, eval=FALSE}
-library(devtools)
-install_github('lebebr01/highlightHTML')
+install.packages("highlightHTML")
 ```
+
+or the development version with devtools:
+```{r devtools, eval = FALSE}
+devtools::install_github('lebebr01/highlightHTMl')
+```
+
+## Usage
 
@@
 library(hightlightHTML)
-highlight_html(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
+file <- system.file('examples', 'bgtable.html', 
+                    package = 'highlightHTML')
+
+tags <- c("#bgred {background-color: #FF0000;}", 
+  "#bgblue {background-color: #0000FF;}")
+
+highlight_html(input = file, 
+               output = tempfile(fileext = ".html"), 
+               tags = tags,
+               update_css = TRUE, 
+               browse = TRUE,
+               print = FALSE)
 ```
@@
 The file is then save to the output location, if no output location is given, the input file will be overwritten.
+
+## Vignette
+Additional examples can be found in the vignette called, The Basics.
+This file give more information and examples.
+The vignette should come with the package when installed from CRAN, however, if you are using the developmental version from GitHub, you may need to tell the installer to build the vignette directly:
+
+```{r build_vignette, eval = FALSE}
+devtools::install_github('lebebr01/highlightHTML', build_vignettes = TRUE)
+```

### 2017-11-29 inst/joss/reviewer_response.md
Improved documentation based on JOSS review

Review Response
-----------

Thanks @daattali for the thoughtful comments and suggestions. In general the following aspects have been adjusted in view of your comments. The README has been significantly adjusted to better reflect the purpose of the package and more typical use cases. The vignette has also been expanded to discuss the `table_id_inject` function in more detail and the source of the input file is shown. Lastly, the code has been adjusted to help improve debugging (i.e. more informative names internally, `&` changed to `&&` where relevant). More specifics are given below in each of these three areas.

## README

- First 6 bullets are related and bundled here. In general the README has been reworked significantly. The introduction to the package has been clarified and expanded slightly to better discuss what I view is a typical use of the package. Some of this has been borrowed from the paper.md JOSS submission. The trivial example has been replaced with a more typical workflow from Rmd to HTML directly with the functions in the package, this is shown in the section "Simple Example of Package Workflow". In the example, I show the raw input Rmd file, the look of the intermediate markdown table with included CSS ids, and then the final code step to compile the document into an HTML. Finally, a screenshot is included to show the look of the final output. I also attempted to change "table" in a few places to "summary table" to reflect the type of table that I feel should be passed to the `table_id_inject` function.
- Added line to README about installation of devtools package.
- Fixed `library(hightlightHTML)` typo.
- The example with `bgtable.html` was removed as this was a contrived example, primarily for testing. A newer example from Rmd to HTML was created to reflect the most useful use case for the package. This file is called `joss.Rmd`.
- The code should be `update_css`. This typo has been fixed from an older version of the package.
- `update_css = FALSE` is mainly used internally and as such has been removed from the master `highlight_html` function, instead just passed internally to the two `highlight_html_cells` and `highlight_html_text` functions.
- Great suggestion on not overwriting input file. This has been remedied to include a warning if the output file location is not specified and the output is then "<input>_out.html".
- Updated package DESCRIPTION to better reflect package goals and maintain consistency with README documentation.

## Vignette

- The GitHub tagline has been edited as well as the README to better reflect the scope of the package and typical use case.
- More time in vignette is given to the `table_id_inject` function. 
- Similar to the README, the raw input file is shown for the typical example.

## Code

- Included better/more tests. This is an area I have improved on since this package was frozen for JOSS review.
- Internal names were replaced to more descriptive names to help improve debugging in the future. Very useful suggestion.
- Adjusted `rgb2hex` function documentation to reflect named vs unnamed list specification.
- Added error handling to catch double NULL case for `rgb2hex` function.
- Switched code where relevant to `&&` instead of `&`. I wasn't aware of the difference actually. Thanks for pointing this out.
- Attempted to clarify the input for the `table_id_inject` function to: A summary table object, most commonly will be a data.frame, but can also be a count table using the `table` function. Let me know if this is more clear.
- `conditions`: additional examples are given and added documentation within the details section to operations that are allowed and which are allowed for each type of variable. 
- Note: I added a rather simple functionality to the `table_id_inject` function. This function now allows for rounding of numeric columns. A by product of the CSS id insertion is that the columns are converted to text. This makes it more difficult to round numeric values to a specific number of decimal places. This feature has been added as an optional argument to the `table_id_inject` function called `num_digits`. This argument takes a single numeric integer that is passed to the `round` function within R.

### 2017-11-29 inst/examples/joss.Rmd
Update example.
Improved documentation based on JOSS review

--- 2017-01-31 inst/examples/joss.Rmd
@@
 
-```{r symm, echo = FALSE}
+```{r symm, echo = FALSE, results = 'asis', message = FALSE}
 library(dplyr)
@@
 
-chick_tab <- chickwts %>%
+chickwts %>%
   group_by(feed) %>%
   summarise(avg_weight = mean(weight),
-            sd_weight = sd(weight))
-
-table_id_inject(chick_tab, id = c('#bggrey', '#bgblack'), 
-                conditions = c('> 270', '> 300'),
-                variable = list('avg_weight', 'avg_weight'))
+            sd_weight = sd(weight)) %>%
+  mutate(feed = as.character(feed)) %>%
+  table_id_inject(id = c('#bggrey', '#bgblack', '#bglightred', '#textblue'), 
+                conditions = c('> 270', '> 300', '> 60', '== "horsebean"'),
+                variable = list('avg_weight', 'avg_weight', 'sd_weight', 'feed'),
+                num_digits = 3) %>%
+  knitr::kable(format = 'markdown')
 ```

### 2017-11-29 readme.Rmd
Improved documentation based on JOSS review

--- 2017-01-03 readme.Rmd
@@
 
-The aim of the `highlightHTML` package is to make it easy for users to customize HTML tables by using a single function that adds an `id` selector to the table cell tag.
+The aim of the `highlightHTML` package is to add some additional formatting to (R)markdown documents to customize the formatting output of HTML files.
+The syntax uses HTML `id` selectors and Cascading Style Sheets (CSS) specified by the user to add formatting to the HTML output file.
 The ability to customize the HTML table is limited the functionality of CSS and the user knowledge of CSS.
-This package was motivated by latest push of using markdown documents which allow the user to focus on content instead of using something like LaTeX where choices between fonts and styling may take a larger role.
-This package is motivated by that in that it allows a seemless way to interact with an HTML file to add table decoration.
+
+The hightlightHTML package fits nicely into the workflow of a reproducible research report as the package can dynamically insert the ids into summary tables with R code.
+In addition, text can be modified directly with simple syntax.
+Compilation from rmarkdown or markdown to HTML can be done directly from the package which makes use of the render function from the rmarkdown package.
+Installation and usage details are shown in more detail below.
+
+## Installation 
+Installing the package:
+```{r install, eval=FALSE}
+install.packages("highlightHTML")
+```
+
+or the development version with devtools:
+```{r devtools, eval = FALSE}
+install.packages("devtools")
+devtools::install_github('lebebr01/highlightHTMl')
+```
 
 ## Usage
-Installing the package:
-```{r install, eval=FALSE}
-library(devtools)
-install_github('lebebr01/highlightHTML')
+
+As mentioned above, text and summary tables can be formatted using CSS ids.
+The CSS ids are inserted into text by using braces (i.e.
+\{) with a CSS id hashtag following the opening brace (e.g.
+\{#bggrey example\}).
+In the previous example, the word "example" would be identified with the CSS id #bggrey and could be formated using CSS.
+
+There are two ways to create formatting within a markdown summary table.
+One is useful if the markdown summary table is created manually (i.e.
+type by hand).
+In this scenario you simply need to add the hashtag to the desired cell of the summary table.
+Perhaps the more common workflow for adding hashtags to a summary table would be dynamically with R code.
+To do this, the function `table_id_inject` is used to create conditional arguments for adding the hashtags to a markdown summary table.
+This is shown in more detail with the example below.
+
+## Simple Example of Package Workflow
+
+Below is a simple example of an Rmd document that combines both elements, text markup and inserting CSS ids dynamically into a table using R code and the `table_id_inject` function.
+
+````
+---
+title: "Rmd to HTML"
+author: "Brandon LeBeau"
+date: "January 13, 2017"
+output: html_document
+---
+
+## Simple Markup
+The `highlightHTML` packages allows for {#bggrey simple markup} to add formatting to text and tables.
+Using the `rmarkdown` package and the `table_id_inject` function allows users to easily add markup to Rmd documents and render directly to HTML.
+
+```{r symm, echo = FALSE, results = 'asis', message = FALSE}`r ''`
+library(dplyr)
+library(highlightHTML)
+
+chickwts %>%
+  group_by(feed) %>%
+  summarise(avg_weight = mean(weight),
+            sd_weight = sd(weight)) %>%
+  mutate(feed = as.character(feed)) %>%
+  table_id_inject(id = c('#bggrey', '#bgblack', '#bglightred', '#textblue'), 
+                conditions = c('> 270', '> 300', '> 60', '== "horsebean"'),
+                variable = list('avg_weight', 'avg_weight', 'sd_weight', 'feed'),
+                num_digits = 3) %>%
+  knitr::kable(format = 'markdown')
+```
+````
+
+The resulting summary table would look like the following in markdown:
+```{r symm, echo = FALSE, results = 'asis', message = FALSE}
+library(dplyr)
+library(highlightHTML)
+
+chickwts %>%
+  group_by(feed) %>%
+  summarise(avg_weight = mean(weight),
+            sd_weight = sd(weight)) %>%
+  mutate(feed = as.character(feed)) %>%
+  table_id_inject(id = c('#bggrey', '#bgblack', '#bglightred', '#textblue'), 
+                conditions = c('> 270', '> 300', '> 60', '== "horsebean"'),
+                variable = list('avg_weight', 'avg_weight', 'sd_weight', 'feed'),
+                num_digits = 3) %>%
+  knitr::kable(format = 'markdown')
 ```
 
-This package post processes the html file produced from a markdown document.  Suppose you have a table like the following:
+It is worth discussing the `table_id_inject` function in more detail here.
+The function takes two required arguments, `id` and `conditionals` and two optional arguments, `variable` and `num_digits`.
+The two required arguments are a vector of CSS ids (e.g.
+#bggrey) and a vector of conditional expressions that are evaluated to identify the location to insert the CSS id.
+These two arguments must be the same length and the CSS id and conditional expression are matched by location.
+That is, the first element of each argument are matched, the second element of each, and so on.
+The optional argument, `variable`, specifies which column(s) of the data to evaluate the conditional expression on.
+By default this argument is empty meaning that all columns are evaluated.
+If a CSS id is specific to a specific column(s), this argument specified as a list can be included.
+Finally, the optional `num_digits` argument is used to round the numeric columns.
+See `round` for more details.
 
-Color Name | Number
------------ | ------------
-Blue | 5
-Green | 35
-Orange | 100
-Red | 200
-
-To use this package there are two steps, first indicate which cells you would like to change the appearance using CSS (i.e.
-background color, text color, etc.) by including the name of the id value to pass that cell or cells.
-Using the above table example suppose we want to change the number column to blue and red for numbers less than 10 and greater than 150 respectively:
-
-Color Name | Number
------------ | ------------
-Blue | 5 #bgblue
-Green | 35
-Orange | 100
-Red | 200 #bgred
-
-The addition of the *#bgblue* and *#bgred* indicates which cells will be changed.
-After turning the markdown document into an html file, this package can now be used to post-process the html file.
-The post-processing will add an id value for each cell with the *#bgblue* or *#bgred* and remove those from the table.
-This will look something like:
+Finally, the Rmd file itself can be passed to the `highlight_html` function which will automatically compile the input file into an HTML output file.
+The `highlight_html` function takes three main arguments, the path to the input Rmd file (can also be a markdown or HTML file), the path to save the output HTML file, and the CSS styling to be used for the formatting.
+Below is the example of processing the simple example shown above.
 
 ```{r function, eval=FALSE}
-library(hightlightHTML)
-highlight_html(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
+library(highlightHTML)
+file <- system.file('examples', 'joss.Rmd', package = 'highlightHTML')
+
+tags <- c('#bgblack {background-color: black; color: white;}',
+          '#bggrey {background-color: #d3d3d3;}',
+          '#bglightred {background-color: #FF6666;}',
+          '#textblue {color: blue}')
+
+highlight_html(input = file, output = tempfile(fileext = ".html"),
+               tags = tags, browse = TRUE, 
+               render = TRUE)
 ```
 
-This function should read in the html file to process.
-Then it processes the file add the id tags to the specific cells identified.
-Lastly if **updateCSS = TRUE**, then the tags will be added to the CSS of the document, otherwise if **FALSE** that will need to be added manually to the html file.
-The file is then save to the output location, if no output location is given, the input file will be overwritten.
+The results HTML output file now looks like the following:
+
+![joss output](inst/examples/joss_output.png)
+
+Finally, the `highlight_html` function has an optional argument called `browse`.
+This argument is a TRUE/FALSE flag, which defaults to TRUE, to indicate whether the HTML output file should be opened in the default browser upon successful compilation.
+This can be a good way to view the file to ensure the desired formatting was achieved.
+
+## Vignette
+Additional examples can be found in the vignette called, The Basics. This file give more information and examples. The vignette should come with the package when installed from CRAN.
+
+```{r vignette, eval = FALSE}
+vignette('the_basics', package = 'highlightHTML')
+```
+
+If you are using the developmental version from GitHub, you may need to tell the installer to build the vignette directly:
+
+```{r build_vignette, eval = FALSE}
+devtools::install_github('lebebr01/highlightHTML', build_vignettes = TRUE)
+```

### 2017-11-29 R/highlightHTML.r

@@ -1,4 +1,4 @@
-highlight_html_cells <- function(x, output, tags, update_css = TRUE, 
+highlight_html_cells <- function(input, output, tags, update_css = TRUE, 
                                  browse = TRUE, print = FALSE) {
   
   CSSid <- gsub("\\{.+", "", tags)
@@ -8,20 +8,20 @@ highlight_html_cells <- function(x, output, tags, update_css = TRUE,
   
   ids <- paste("<td id='", CSSidPaste, "'", sep = "")
   
-  for(i in 1:length(CSSid)){
-    locations <- grep(CSSid[i], x)  # finds locations to add id values
-    x[locations] <- gsub("<td", ids[i], x[locations])  # adds the id values
-    x[locations] <- gsub(CSSid2[i], "", x[locations], fixed = TRUE)
+  for(i in seq_along(CSSid)){
+    locations <- grep(CSSid[i], input)  # finds locations to add id values
+    input[locations] <- gsub("<td", ids[i], input[locations])  # adds the id values
+    input[locations] <- gsub(CSSid2[i], "", input[locations], fixed = TRUE)
   }
   
   if(update_css){
-    x <- update_css(x, tags)
+    input <- update_css(input, tags)
   }
   
   if(print) {
-    x
+    input
   } else {
-    write(x, file = output)
+    write(input, file = output)
     if(browse) {
       browseURL(output)
     } 
@@ -29,7 +29,7 @@ highlight_html_cells <- function(x, output, tags, update_css = TRUE,
 }
 
 #' @importFrom utils browseURL
-highlight_html_text <- function(x, output, tags, update_css = TRUE, 
+highlight_html_text <- function(input, output, tags, update_css = TRUE, 
                                 browse = TRUE, print = FALSE){
   
   CSSid <- gsub("\\{.+", "", tags)
@@ -39,20 +39,20 @@ highlight_html_text <- function(x, output, tags, update_css = TRUE,
   
   ids <- paste("<span id='", CSSidPaste, "'>", sep = "")
   
-  for(i in 1:length(CSSid)){
-    locations <- grep(CSSid[i], x)  # finds locations to add id values
-    x[locations] <- gsub(paste("\\{", CSSid[i], sep = ''), ids[i], x[locations])  # adds the id values
-    x[locations] <- gsub("\\}", "</span>", x[locations])
+  for(i in seq_along(CSSid)){
+    locations <- grep(CSSid[i], input)  # finds locations to add id values
[…]

### 2017-11-29 R/highlightHTMLmaster.r

@@ -1,23 +1,23 @@
 #' Master highlight HTML function
 #' 
-#' This function inputs and exports an HTML file.  The HTML file is then processed
-#' to search for tags that inject CSS automatically into the HTML file.
+#' This function inputs a markdown or rmarkdown document and exports an HTML file. 
+#' The HTML file is then processed to search for tags that inject CSS automatically 
+#' into the HTML file.
 #' 
-#' A function that allows the alteration of HTML using CSS.  This may be helpful
+#' A function that allows the alteration of HTML using CSS. This may be helpful
 #' coming from a markdown or R markdown file to alter aspects of the page based on 
-#' a specific criteria.  This function handles both tables as well as normal text.  
+#' a specific criteria. This function handles both tables as well as normal text.  
 #' The options are only limited based on your knowledge of CSS.
 #' 
-#' @param input File name of HTML file to highlight the cells of the table or text. 
-#'    Alternatively, if render = TRUE, a Rmd or md file can be specified as the input.
+#' @param input File name of markdown or rmarkdown file to highlight the cells of the table or text. 
+#'    Alternatively, if render = FALSE, a HTML file can be specified as the input.
 #' @param output Output file name of highlighted HTML file
 #' @param tags character vector with CSS tags to be added
-#' @param update_css TRUE/FALSE variable indicating whether the CSS should be updated
 #' @param browse logical, If TRUE (default) output file opens in default browser, if FALSE, 
 #'    file is written, but not opened in browser. 
 #' @param print logical, if TRUE print output to R console, if false (default) output is 
 #'    filtered to other methods (see browse or output).
-#' @param render logical, if TRUE will call the rmarkdown::render() function to 
+#' @param render logical, if TRUE (default) will call the rmarkdown::render() function to 
 #'    convert Rmd or md files to html prior to injecting CSS.
 #' @examples
 #' \donttest{
@@ -36,7 +36,7 @@
 #'   
 #' # Command to post-process HTML file - Writes to temporary file
 #' highlight_html(input = file, output = tempfile(fileext = ".html"),  
-#'   tags = tags, update_css = TRUE, browse = FALSE)
+#'   tags = tags, browse = FALSE)
 #'   
 #' # Change background color and text color with CSS
[…]

### 2017-11-29 R/rgb2hex.r

@@ -3,8 +3,9 @@
 #' Enter a list of RGB color codes, or R colors, and get the appropriate hex color code.
 #' 
 #' @param rgbcode List of rgb color codes, each list must be a vector of three objects representing
-#'   the three components of rgb color code from 0 - 255.
-#' @param rcolor A list of R color names
+#'   the three components of rgb color code from 0 - 255. This can be a named list where the name
+#'   represents the name of the color to be used.
+#' @param rcolor An unnamed list of R color names.
 #' @examples 
 #' rgb2hex(rcolor = list("sienna2", "thistle1"))
 #' rgb2hex(rcolor = list("sienna2", "thistle1"), rgbcode = list('orange' = c(238, 74, 24), 
@@ -14,13 +15,17 @@
 #' @export 
 rgb2hex <- function(rgbcode = NULL, rcolor = NULL) {
   
-  if(!is.null(rcolor)){
-    if(!is.list(rcolor)) { rcolor <- as.list(rcolor) }
-    tmp <- lapply(lapply(rcolor, col2rgb), as.numeric)
+  if(is.null(rgbcode) && is.null(rcolor)) {
+    stop("Must specify at least one RGB Code or an R color name")
   }
   
-  if(is.null(rcolor) & !is.null(rgbcode)){ 
-    tmp <- rgbcode 
+  if(!is.null(rcolor)){
+    if(!is.list(rcolor)) { rcolor <- as.list(rcolor) }
+    rgb_codes <- lapply(lapply(rcolor, col2rgb), as.numeric)
+  }
+  
+  if(is.null(rcolor) && !is.null(rgbcode)){ 
+    rgb_codes <- rgbcode 
   }
   
   if(is.null(names(rgbcode))) {
@@ -29,18 +34,18 @@ rgb2hex <- function(rgbcode = NULL, rcolor = NULL) {
     namescol <- names(rgbcode)
   }
   
-  if(!is.null(rcolor) & !is.null(rgbcode)){
-    tmp <- c(rgbcode, tmp)
+  if(!is.null(rcolor) && !is.null(rgbcode)){
+    rgb_codes <- c(rgbcode, rgb_codes)
     namescol <- c(names(rgbcode), rcolor)
   }
   
-  if(!is.null(rcolor) & is.null(rgbcode)){
+  if(!is.null(rcolor) && is.null(rgbcode)){
     namescol <- rcolor
   }  
   
[…]

### 2017-11-29 R/table_inject.r

@@ -1,47 +1,87 @@
-#' Table hash addition
+#' Table hash addition for markup
 #' 
-#' A helper function to include a hashtag id code within an R table.
+#' A helper function to include a hashtag id code within a summary table. The summary table 
+#' most commonly will take the form of a data frame object. For example,
+#' a descriptive summary table coming from the \code{summarise} function from  
+#' the dplyr package. Can also specify a count table using the \code{table} function.
 #' 
-#' @param x A table object
+#' The \code{conditions} argument takes the following operators for numeric variables: 
+#' \code{>}, \code{>=}, \code{<}, \code{<=}, \code{==}. For character variables, 
+#' only \code{==} can be used to specify the text string to match on. Care needs to be 
+#' made to wrap ensure the text string is wrapped in quotations. See the examples 
+#' for more details on this.
+#' 
+#' This function can also be part of a chain using the \code{\%>\%} operator from magrittr. 
+#' See the examples for more details.
+#'  
+#' 
+#' @param table A summary table object, most commonly will be a data.frame, but can also
+#'   be a count table using the \code{table} function.
 #' @param id A vector of css id(s) to include
-#' @param conditions A vector of conditions to include id. Must be same length as id
+#' @param conditions A character vector of conditions to include id. Must be same length as id. See 
+#'   details and examples for more information on how to specify the conditions.
 #' @param variable An optional list of column names to specify search of conditions. More
 #'      than one variable can be specified in each element of the list. The list must be the 
 #'      same length as the conditions or id arguments.
+#' @param num_digits A numeric value to specify the number of decimal values to 
+#'   include in the final output.
 #' @export
 #' 
 #' @examples 
 #' library(dplyr)
 #' library(highlightHTML)
 #'
-#' summ_table <- mtcars %>% 
+#' mtcars %>% 
 #'   group_by(cyl) %>% 
 #'   summarise(avg_mpg = mean(mpg), sd_mpg = sd(mpg)) %>%
-#'   data.frame()
[…]

### 2017-11-29 R/util.r

@@ -1,12 +1,12 @@
-update_css <- function(x, tags) {
+update_css <- function(html_file, tags) {
   
-  location <- max(grep("</style>", x, ignore.case = TRUE))
+  location_css <- max(grep("</style>", html_file, ignore.case = TRUE))
   
   # # split file
-  tmpA <- x[1:(location - 1)]
-  tmpB <- x[location:length(x)]
+  html_preamble <- html_file[1:(location_css - 1)]
+  html_main <- html_file[location_css:length(html_file)]
   
   ## adding custom CSS
-  tmp <- c(tmpA, tags, tmpB)
-  tmp
+  updated_html <- c(html_preamble, tags, html_main)
+  updated_html
 }

### 2017-11-29 tests/testthat/test_rgb.r

@@ -6,3 +6,7 @@ test_that('correct structure', {
                             rgbcode = list('orange' = c(238, 74, 24),
                                            'raw umber' = c(113, 75, 35)))), 4)
 })
+
+test_that("error parsing", {
+  expect_error(rgb2hex())
+})

### 2017-11-29 tests/testthat/test_structure.r

@@ -1,4 +1,4 @@
-context('test structure')
+context('test tag insertion')
 
 test_that('correct print structure', {
   file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
@@ -9,7 +9,14 @@ test_that('correct print structure', {
             "#colgreen {color: green;}")
   
   # Post-process HTML file
-  tmp <- highlight_html(input = file, output = tempfile(fileext = ".html"), update_css = TRUE, 
-                 tags = tags, browse = FALSE, print = TRUE)
-  expect_true(is.character(tmp))
+  text_output <- highlight_html(input = file, output = tempfile(fileext = ".html"), 
+                 tags = tags, browse = FALSE, print = TRUE, render = FALSE)
+  
+  expect_true(any(grepl("#bgblack", text_output)))
+  expect_true(any(grepl("#bgblue", text_output)))
+  expect_true(any(grepl("#colgreen", text_output)))
+  
+  expect_true(any(grepl("id='bgblack'", text_output)))
+  expect_true(any(grepl("id='bgblue'", text_output)))
+  expect_true(any(grepl("id='colgreen'", text_output)))
 })

### 2017-11-29 tests/testthat/test_table_id.r

@@ -2,30 +2,33 @@ context('table_id_inject')
 
 test_that('add in tags to table', {
   library(dplyr)
+  
   summ_table <- mtcars %>% 
     group_by(cyl) %>% 
     summarise(avg_mpg = mean(mpg), sd_mpg = sd(mpg)) %>%
     data.frame()
   
-  tmp <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+  inject_table <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
                   conditions = c('< 2', '> 16'))
   
-  expect_true(grepl('#bgblue', tmp['avg_mpg']))
-  expect_true(grepl('#bgred', tmp['sd_mpg']))
+  expect_true(grepl('#bgblue', inject_table['avg_mpg']))
+  expect_true(grepl('#bgred', inject_table['sd_mpg']))
   
-  tmp <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+  inject_table <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
                          conditions = c('< 2', '< 16'),
                          variable = list(c('sd_mpg'), c('avg_mpg')))
-  expect_true(grepl('#bgblue', tmp['avg_mpg']))
-  expect_true(grepl('#bgred', tmp['sd_mpg']))
-  expect_false(grepl('#bgblue', tmp['sd_mpg']))
   
-  tmp <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+  expect_true(grepl('#bgblue', inject_table['avg_mpg']))
+  expect_true(grepl('#bgred', inject_table['sd_mpg']))
+  expect_false(grepl('#bgblue', inject_table['sd_mpg']))
+  
+  inject_table <- table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
                          conditions = c('< 2', '< 16'),
                          variable = list(c('sd_mpg'), c('avg_mpg', 'sd_mpg')))
-  expect_true(grepl('#bgblue', tmp['avg_mpg']))
+  
+  expect_true(grepl('#bgblue', inject_table['avg_mpg']))
   #expect_false(grepl('#bgred', tmp['sd_mpg']))
-  expect_true(grepl('#bgblue', tmp['sd_mpg']))
+  expect_true(grepl('#bgblue', inject_table['sd_mpg']))
   
   
 })

### 2017-11-29 vignettes/the_basics.R

@@ -7,9 +7,9 @@
 #  highlight_html(input = file,
 #                 output = tempfile(fileext = ".html"),
 #                 tags = tags,
-#                 update_css = TRUE,
 #                 browse = TRUE,
-#                 print = FALSE)
+#                 print = FALSE,
+#                 render = FALSE)
 
 ## ----text, eval = FALSE--------------------------------------------------
 #  file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
@@ -21,16 +21,33 @@
 #  
 #  # Post-process HTML file
 #  highlight_html(input = file, output = tempfile(fileext = ".html"),
-#                 tags = tags, update_css = TRUE, browse = TRUE)
+#                 tags = tags, browse = TRUE, render = FALSE)
 
-## ----html, eval = FALSE--------------------------------------------------
+## ----symm, echo = FALSE, results = 'asis', message = FALSE---------------
+library(dplyr)
+library(highlightHTML)
+
+chickwts %>%
+  group_by(feed) %>%
+  summarise(avg_weight = mean(weight),
+            sd_weight = sd(weight)) %>%
+  mutate(feed = as.character(feed)) %>%
+  table_id_inject(id = c('#bggrey', '#bgblack', '#bglightred', '#textblue'), 
+                conditions = c('> 270', '> 300', '> 60', '== "horsebean"'),
+                variable = list('avg_weight', 'avg_weight', 'sd_weight', 'feed'),
+                num_digits = 3) %>%
+  knitr::kable(format = 'markdown')
+
+## ----joss_compile, eval=FALSE--------------------------------------------
+#  library(highlightHTML)
 #  file <- system.file('examples', 'joss.Rmd', package = 'highlightHTML')
 #  
 #  tags <- c('#bgblack {background-color: black; color: white;}',
 #            '#bggrey {background-color: #d3d3d3;}',
-#            '#bglightred {background-color: #FF6666;}')
+#            '#bglightred {background-color: #FF6666;}',
+#            '#textblue {color: blue}')
 #  
 #  highlight_html(input = file, output = tempfile(fileext = ".html"),
-#                 tags = tags, update_css = TRUE, browse = TRUE,
+#                 tags = tags, browse = TRUE,
 #                 render = TRUE)
 

### 2017-11-29 inst/joss/reviewer_response.md
Updated review response and switched warning to message

@@
 I also attempted to change "table" in a few places to "summary table" to reflect the type of table that I feel should be passed to the `table_id_inject` function.
+I'd be interested in feedback on whether this is both easier to read and offers a more compelling use/workflow for the package.
 - Added line to README about installation of devtools package.
@@
 This file is called `joss.Rmd`.
-- The code should be `update_css`. This typo has been fixed from an older version of the package.
-- `update_css = FALSE` is mainly used internally and as such has been removed from the master `highlight_html` function, instead just passed internally to the two `highlight_html_cells` and `highlight_html_text` functions.
-- Great suggestion on not overwriting input file. This has been remedied to include a warning if the output file location is not specified and the output is then "<input>_out.html".
+- `update_css = FALSE` is used internally and as such has been removed from the master `highlight_html` function, instead just passed internally to the two `highlight_html_cells` and `highlight_html_text` functions.
+Discussion of this argument has also been removed from the README and vignette.
+- Great suggestion on not overwriting input file.
+This has been remedied to include a message if the output file location is not specified and the output is then "<input>_out.html".
+The file path of the generated output file is included in the printed message.
 - Updated package DESCRIPTION to better reflect package goals and maintain consistency with README documentation.
@@
 
-- Included better/more tests. This is an area I have improved on since this package was frozen for JOSS review.
+- Adjusted tests.
+This is an area I have commonly struggled with implementation.
+I believe the tests are a bit more helpful to help distinguish whether specific features are working.
+I am now testing whether the CSS tags and ids are found within the output document.
+I'm open to any additional tests you think about be useful here.
 - Internal names were replaced to more descriptive names to help improve debugging in the future. Very useful suggestion.
@@
 Let me know if this is more clear.
-- `conditions`: additional examples are given and added documentation within the details section to operations that are allowed and which are allowed for each type of variable. 
+- `conditions`: additional examples are given and added documentation within the details section to operations that are allowed and which are allowed for each type of variable (i.e.
+which are allowed for numeric vs categorical).
 - Note: I added a rather simple functionality to the `table_id_inject` function.

### 2017-11-29 R/highlightHTMLmaster.r

@@ -78,8 +78,8 @@
 highlight_html <- function(input, output, tags, browse = TRUE, print = FALSE,
                            render = TRUE) {
   if(missing(output)) {
-    warning("output file name not specified, defaults to <input>_out.html")
     output <- gsub("\\.md$|\\.Rmd", "_out\\.html", input)
+    message("output file path not specified, file saved to ", output)
   }
   
   if(render) {

### 2017-11-30 readme.Rmd
Update to README/vignette to improve readability

@@
 
-The aim of the `highlightHTML` package is to add some additional formatting to (R)markdown documents to customize the formatting output of HTML files.
-The syntax uses HTML `id` selectors and Cascading Style Sheets (CSS) specified by the user to add formatting to the HTML output file.
-The ability to customize the HTML table is limited the functionality of CSS and the user knowledge of CSS.
+The highlightHTML package adds markdown syntax to allow for additional styling of (R)markdown documents with HTML output files.
+The syntax uses HTML id selectors and Cascading Style Sheets (CSS) specified by the user to add the desired style to the HTML output file.
+The ability to customize the HTML file is limited by the user knowledge of CSS and the ability of CSS to style a given element.
 
@@
 
-As mentioned above, text and summary tables can be formatted using CSS ids.
+As mentioned above, text and summary tables can be styled using CSS ids.
 The CSS ids are inserted into text by using braces (i.e.
@@
 \{#bggrey example\}).
-In the previous example, the word "example" would be identified with the CSS id #bggrey and could be formated using CSS.
+In the previous example, the word "example" would be identified with the CSS id #bggrey and could be styled using CSS.
 
-There are two ways to create formatting within a markdown summary table.
-One is useful if the markdown summary table is created manually (i.e.
+There are two ways to create styling within a markdown summary table.
+The first option is useful if the markdown summary table is created manually (i.e.
 type by hand).
@@
 Below is a simple example of an Rmd document that combines both elements, text markup and inserting CSS ids dynamically into a table using R code and the `table_id_inject` function.
+The summary table below is calculating the mean and standard deviation of the chick weights by different feed types.
+You can imagine creating a similar table in reports that you create.
 
@@
 ## Simple Markup
-The `highlightHTML` packages allows for {#bggrey simple markup} to add formatting to text and tables.
+The `highlightHTML` packages allows for {#bggrey simple markup} to add styling to text and tables.
 Using the `rmarkdown` package and the `table_id_inject` function allows users to easily add markup to Rmd documents and render directly to HTML.
@@
 The optional argument, `variable`, specifies which column(s) of the data to evaluate the conditional expression on.
-By default this argument is empty meaning that all columns are evaluated.
-If a CSS id is specific to a specific column(s), this argument specified as a list can be included.
+By default this argument is empty meaning that the conditional expressions are evaluated on every column.
+If a CSS id is specific to a specific column(s), this argument, specified as a list, can be included to limit the conditional expression to be evaluated on only the column(s) of interest.
 Finally, the optional `num_digits` argument is used to round the numeric columns.
@@
 Finally, the Rmd file itself can be passed to the `highlight_html` function which will automatically compile the input file into an HTML output file.
-The `highlight_html` function takes three main arguments, the path to the input Rmd file (can also be a markdown or HTML file), the path to save the output HTML file, and the CSS styling to be used for the formatting.
-Below is the example of processing the simple example shown above.
+The `highlight_html` function takes three main arguments, the path to the input Rmd file (can also be a markdown or HTML file), the path to save the output HTML file, and the CSS styling to be used for the styling Below is the example of processing the simple example shown above.
 
@@
 highlight_html(input = file, output = tempfile(fileext = ".html"),
-               tags = tags, browse = TRUE, 
-               render = TRUE)
+               tags = tags, browse = TRUE, render = TRUE)
 ```
 
-The results HTML output file now looks like the following:
+The resulting HTML file now looks like the following:
 
@@
 This argument is a TRUE/FALSE flag, which defaults to TRUE, to indicate whether the HTML output file should be opened in the default browser upon successful compilation.
-This can be a good way to view the file to ensure the desired formatting was achieved.
+This can be a good way to view the file to ensure the desired styling was achieved.
 

### 2018-01-11 readme.Rmd
Updates based on reviewer comments #5

@@
 install.packages("devtools")
-devtools::install_github('lebebr01/highlightHTMl')
+devtools::install_github('lebebr01/highlightHTML')
 ```
@@
 
-As mentioned above, text and summary tables can be styled using CSS ids.
-The CSS ids are inserted into text by using braces (i.e.
+As mentioned above, text and summary tables can be styled using CSS ids or classes.
+The CSS ids (or classes) are inserted into text by using braces (i.e.
 \{) with a CSS id hashtag following the opening brace (e.g.
-\{#bggrey example\}).
+`\{#bggrey example\}`).
 In the previous example, the word "example" would be identified with the CSS id #bggrey and could be styled using CSS.
@@
 
-## Simple Example of Package Workflow
+## Adding CSS ids manually
+Suppose you have a summary table like the following (note: this table was created by typing manually, a more typical workflow is shown later using R directly):
+
+| Color Name | Number       |
+|----------- | ------------ |
+| Red        |  25          |
+| Blue       |  40          |
+| Green      |  4           |
+| Orange     |  87          |
+
+You could then add styling by adding the following tags to the table, again this was added by hand, but a conditional example with R is shown later.
+
+| Color Name | Number       |
+|----------- | ------------ |
+| Red        |  25  #bgred  |
+| Blue       |  40  #bgblue |
+| Green      |  4           |
+| Orange     |  87          |
+
+The addition of the *#bgblue* and *#bgred* indicates which cells will be changed.
+After turning the markdown document into an html file, this package can now be used to post-process the html file.
+The post-processing will add an id value for each cell with the *#bgblue* or *#bgred* and remove those from the table.
+
+The CSS for these ids could be as simple as the following to change the background color of the cells with the CSS id inserted above:
+
+````
+#bgred {background-color: #FF0000;}
+#bgblue {background-color: #0000FF;}
+````
+
+## Simple Example of Common Package Workflow
 

### 2018-01-11 R/table_inject.r

@@ -64,6 +64,16 @@
 
 table_id_inject <- function(table, id, conditions, variable = NULL, num_digits = NULL) {
   
+  if(length(id) != length(conditions)) {
+    stop("The arguments id and conditions must be the same length")
+  }
+  
+  if(!is.null(variable)) {
+    if(length(id) != length(variable)) {
+      stop("The arguments id and variable must be the same length")
+    }
+  }
+  
   if(!is.null(num_digits)) {
     numeric_columns <- unlist(lapply(table, is.numeric))
     table[numeric_columns] <- round(table[numeric_columns], num_digits)

### 2018-01-11 tests/testthat/test_table_id.r

@@ -27,8 +27,14 @@ test_that('add in tags to table', {
                          variable = list(c('sd_mpg'), c('avg_mpg', 'sd_mpg')))
   
   expect_true(grepl('#bgblue', inject_table['avg_mpg']))
-  #expect_false(grepl('#bgred', tmp['sd_mpg']))
   expect_true(grepl('#bgblue', inject_table['sd_mpg']))
   
+  expect_error(table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+                               conditions = c('< 2'),
+                               variable = list(c('sd_mpg'), c('avg_mpg', 'sd_mpg'))))
+  
+  expect_error(table_id_inject(summ_table, id = c('#bgred', '#bgblue'), 
+                               conditions = c('< 2', '< 16'),
+                               variable = list(c('avg_mpg', 'sd_mpg'))))
   
 })

### 2018-01-12 readme.Rmd
Add JOSS badge to README

@@
 [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](http://cran.r-project.org/package=highlightHTML)
+[![DOI](http://joss.theoj.org/papers/10.21105/joss.00185/status.svg)](https://doi.org/10.21105/joss.00185)
 

### 2020-03-20 R/highlightHTMLmaster.r
Remove donttest examples

@@ -20,11 +20,6 @@
 #' @param render logical, if TRUE (default) will call the rmarkdown::render() function to 
 #'    convert Rmd or md files to html prior to injecting CSS.
 #' @examples
-#' \donttest{
-#' # Example of simple test table
-#' # Change background color of table cells
-#' library(highlightHTML)
-#' 
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 
 #' # r console.
@@ -37,43 +32,6 @@
 #' # Command to post-process HTML file - Writes to temporary file
 #' highlight_html(input = file, output = tempfile(fileext = ".html"),  
 #'   tags = tags, browse = FALSE)
-#'   
-#' # Change background color and text color with CSS
-#' tags <- c("#bgred {background-color: #FF0000; color: white;}", 
-#'   "#bgblue {background-color: #0000FF; color: white;}")
-#'   
-#' # Post-process HTML file
-#' highlight_html(input = file, output = tempfile(fileext = ".html"),  
-#'   tags = tags, update_css = TRUE, browse = TRUE, print = FALSE)
-#' 
-#' # By default the new file is opened in your default browser, here set to FALSE
-#' highlight_html(input = file, output = tempfile(fileext = ".html"), 
-#'   tags = tags, browse = FALSE, print = FALSE)
-#'   
-#' # Setting path for example html files 
-#' # To see path where these are saved, type file or file1 in the 
-#' # r console.
-#' file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')
-#' 
-#' # Change background color and text color with CSS
-#' tags <- c("#bgblack {background-color: black; color: white;}", 
-#'   "#bgblue {background-color: #0000FF; color: white;}",
-#'   "#colgreen {color: green;}")
-#'   
-#' # Post-process HTML file
-#' highlight_html(input = file, output = tempfile(fileext = ".html"), 
-#'   tags = tags, browse = TRUE)
-#'   
-#' # Use of render
-#' file <- system.file('examples', 'mwe.md', package = 'highlightHTML')
-#' tags <- c("#bgred {background-color: #FF0000; color: white;}",
-#'    "#bgblue {background-color: #0000FF; color: white;}",
-#'    "#bgblack {background-color: #000000; color: white;}",
-#'    "#colgold {color: #FFD700;}")
-#' highlight_html(input = file, output = tempfile(fileext = '.html'),
[…]

### 2020-03-20 readme.Rmd
Add GA badge

--- 2018-01-11 readme.Rmd
@@
 [![Build Status](https://travis-ci.org/lebebr01/highlightHTML.svg?branch=master)](https://travis-ci.org/lebebr01/highlightHTML)
+[![R build status](https://github.com/lebebr01/highlightHTML/workflows/R-CMD-check/badge.svg)](https://github.com/lebebr01/highlightHTML/actions?workflow=R-CMD-check)
 [![codecov.io](https://codecov.io/github/lebebr01/highlightHTML/coverage.svg?branch=master)](https://codecov.io/github/lebebr01/highlightHTML?branch=master)
 [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](http://cran.r-project.org/package=highlightHTML)
+[![DOI](http://joss.theoj.org/papers/10.21105/joss.00185/status.svg)](https://doi.org/10.21105/joss.00185)
 

### 2020-04-03 readme.Rmd
Add https cran link

--- 2018-01-11 readme.Rmd
@@
 [![Build Status](https://travis-ci.org/lebebr01/highlightHTML.svg?branch=master)](https://travis-ci.org/lebebr01/highlightHTML)
+[![R build status](https://github.com/lebebr01/highlightHTML/workflows/R-CMD-check/badge.svg)](https://github.com/lebebr01/highlightHTML/actions?workflow=R-CMD-check)
 [![codecov.io](https://codecov.io/github/lebebr01/highlightHTML/coverage.svg?branch=master)](https://codecov.io/github/lebebr01/highlightHTML?branch=master)
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](http://cran.r-project.org/package=highlightHTML)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](https://cran.r-project.org/package=highlightHTML)
+[![DOI](http://joss.theoj.org/papers/10.21105/joss.00185/status.svg)](https://doi.org/10.21105/joss.00185)
 

### 2020-04-21 R/highlightHTMLmaster.r
update example, dontrun

@@ -23,6 +23,7 @@
 #' # Setting path for example html files 
 #' # To see path where these are saved, type file or file1 in the 
 #' # r console.
+#' \dontrun{
 #' file <- system.file('examples', 'bgtable.html', package = 'highlightHTML')
 #' 
 #' # Creating CSS tags to inject into HTML document
@@ -30,7 +31,6 @@
 #'   "#bgblue {background-color: #0000FF;}")
 #'   
 #' # Command to post-process HTML file - Writes to temporary file
-#' \dontrun{
 #' highlight_html(input = file, output = tempfile(fileext = ".html"),  
 #'   tags = tags, browse = FALSE)
 #' }
